---
title: "First Assignment (Test)"
author: "Olivia Hudson"
date: "27/01/2020"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = TRUE)
```

## Reading the Data

```{r Reading the Data, message=FALSE, warning=FALSE}
library(tidyverse)
Data <- read_tsv("C:/Users/Liv/OneDrive - University of Exeter/Second Year/Term 2/POL2094 Data Analysis iii/Github/datan3/Data/6614tab_10EB1BA6123C0D95E60D28E156AEA8F7_V1/UKDA-6614-tab/tab/ukhls_w9/i_youth.tab")

```

## Tabulate Variables
 ## There is no variable for gender and so i have used sex instead
```{r Tabulate Variables, message=FALSE, warning=FALSE}
table(Data$i_dvage)
table(Data$i_sex)
table(Data$i_ypsocweb)
``` 
 ## from this we can see that 2277 people answered yes to the question 'Do you belong to any social networking web-sites?', 530 answered no and 14 observations contained missing data. We can also see that 1411 respondents are male and 1410 are female. 
 
## Recode Variables 
We want to create a new binary variable for having an account on social media so that 1 means "yes", 0 means "no", and all missing values are coded as NA. We also want to recode gender into a new variable with the values "male" and "female" (this can be a character vector or a factor).

```{r}
Data$i_ypsocweb[Data$i_ypsocweb == "2"] -> "0" 
Data$i_ypsocweb[Data$i_ypsocweb == "-9"] -> 'NA'
Data$i_sex[Data$i_sex == "1"] -> "male" 
Data$i_sex[Data$i_sex == "2"] -> "female" 
```

##
 